### 2023-01-15 output/DiD/tables/balance_table.tex
Adjusted rows of balance table

\begin{tabular}{llccc}
\toprule
 &  & \textit{} & \multicolumn{2}{|c|}{\textit{Difference in Cases Won by Defendant}} \\
 &  & Cases Won by Plaintiff & Unweighted & P-Value \\
\midrule
\multirow[c]{5}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 \\
 & No cause & 0.04 & 0.03 & 0.00 \\
 & Non-payment of rent & 0.11 & -0.03 & 0.03 \\
 & Defendant has an attorney & 0.72 & -0.01 & 0.77 \\
 & Plaintiff has an attorney & 0.02 & -0.02 & 0.00 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant is an entity & 0.07 & -0.14 & 0.00 \\
 & Plaintiff is an entity & 0.80 & 0.01 & 0.47 \\
 & Total property value & 0.01 & 0.00 & 0.37 \\
 & Building value & 0.66 & 0.03 & 0.13 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Land value & 6554743.50 & 184134.63 & 0.79 \\
 & Other value & 1897711.00 & 25986.91 & 0.90 \\
 & Median household income (2016) & 87585.64 & 22095.39 & 0.21 \\
 & Population density (2010) & 8535625.58 & 232361.89 & 0.78 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median two bedroom rent (2015) & 52087.32 & 2566.82 & 0.01 \\
 & Portion white (2010) & 9031.64 & 944.99 & 0.01 \\
 & rent_twobed2015 & 1093.36 & 34.26 & 0.05 \\
 & share_white2010 & 0.60 & 0.04 & 0.00 \\
\cline{1-5}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccc}
\toprule
 &  & \textit{} & \multicolumn{2}{|c|}{\textit{Difference in Cases Won by Defendant}} & \textit{} \\
 &  & Cases Won by Plaintiff & Unweighted & P-Value & N \\
\midrule
\multirow[c]{3}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.01 & 0.68 & 3298.00 \\
 & No cause & 0.11 & -0.03 & 0.03 & 3298.00 \\
 & Non-payment of rent & 0.72 & -0.01 & 0.77 & 3298.00 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.07 & -0.14 & 0.00 & 3298.00 \\
 & Plaintiff has an attorney & 0.80 & 0.01 & 0.47 & 3298.00 \\
 & Defendant is an entity & 0.01 & 0.00 & 0.37 & 3298.00 \\
 & Plaintiff is an entity & 0.66 & 0.03 & 0.13 & 3298.00 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel D: Assessor Records From Most Recent Pre-Filing F.Y.}} & Building value & 6554743.50 & 184134.63 & 0.79 & 3021.00 \\
 & Land value & 1897711.00 & 25986.91 & 0.90 & 3021.00 \\
 & Other value & 87585.64 & 22095.39 & 0.21 & 3021.00 \\
 & Total property value & 8535625.58 & 232361.89 & 0.78 & 3021.00 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel E: Census Tract Characteristics}} & Median household income (2016) & 52087.32 & 2566.82 & 0.01 & 3297.00 \\
 & Population density (2010) & 9031.64 & 944.99 & 0.01 & 3297.00 \\
 & Median two bedroom rent (2015) & 1093.36 & 34.26 & 0.05 & 2488.00 \\
 & Portion white (2010) & 0.60 & 0.04 & 0.00 & 3297.00 \\
\cline{1-6}
\bottomrule
\end{tabular}
